Draft Exploration

### 2020-04-07 draft_exploration.Rmd
created function to generate plot of peak career outcomes

mlb_percentile_unsigned(round = 20, startyear = 1990, endyear = 2011)
```

>>>>

mlb_percentile_unsigned(round = , startyear = 1990, endyear = 2011)
```

peak_level <- function(max_round, startyear, endyear, min_round = 1) {

top_20_hs <- master %>%
  filter(source == "H" & draft_numb == 1) %>%
  filter(draft_round >= min_round & draft_round <= max_round & year >= startyear & year <= endyear) %>%
  mutate(high_level = ifelse(high_level %in% c("-", "JrCollege", "NAIA", "NCAA"),
                             "<=College",
                             high_level)) %>%
  group_by(signed, high_level) %>%
  summarize(n = n()) %>%
  group_by(signed) %>%
  mutate(y = n/sum(n))

top_20_hs$high_level <- factor(top_20_hs$high_level,levels = c("<=College",
                                                               "Indy",
                                                               "Rk",
                                                               "A-",
                                                               "A",
                                                               "A+",
                                                               "AA",
                                                               "AAA",
                                                               "MLB"))

top_20_hs %>%
  ggplot() +
  geom_col(aes(x = high_level, y = y, fill = signed), position = "dodge") +
  scale_y_continuous(labels = scales::percent_format()) +
  theme_light() +
  labs(
    x = "Peak Baseball Level Reached",
    y = "Percentage",
    signed = "Signed?",
    title = "Distribution of Peak Baseball Career Level of High School Picks",
    subtitle = "Grouped by whether or not the player signed out of high school"
  )

peak_level(max_round = 20, startyear = 1990, endyear = 2011, min_round = 10)
```
